---
title: "$title$"
subtitle: "$subtitle$"
abstract-title: "$abstract_title$"
abstract: "$abstract$"
date: "`r Sys.Date()`"
output: 
  dlookr::dlookr_$theme$_paged: 
    # Change to point to your cover file
    front_cover: $cover$
    toc: true
    # Change to true to add number in front of chapters
    number_sections: false
    # Change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: true
# Set  toc title, default none
toc-title: Contents
#knit: pagedown::chrome_print
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      collapse = FALSE,
                      comment = "#>",
                      fig.align = "center")
knitr::opts_chunk$set(fig.width = 12, fig.height = 9)
```

```{r packages, include=FALSE, message=FALSE, warning=FALSE}
# Load required packages for charts with UNHCR style 
library(dplyr)
library(ggplot2)
library(kableExtra)
library(dlookr)
library(htmltools)
library(reactable)

reportData <- get("reportData", .dlookrEnv)
sample_percent <- get("sample_percent", .dlookrEnv)
author <- get("author", .dlookrEnv)
thres_uniq_cat <- get("thres_uniq_cat", .dlookrEnv)
thres_uniq_num <- get("thres_uniq_num", .dlookrEnv)
base_family <- get("base_family", .dlookrEnv)
```


```{css, echo=FALSE}
.pagedjs_page.pagedjs_first_page .pagedjs_margin-top-right>.pagedjs_margin-content::after {
    content: url("$logo$");
}

.title {
  color: $title_color$;
}

.subtitle {
  color: $subtitle_color$;
  font-size: 2.5em !important;  
}

/* Warnings */
.tag {
  display: inline-block;
  padding: 2px 12px;
  border-radius: 5px;
  font-weight: 600;
  font-size: 12px;
}

.recommand-check {
  background: hsl(116, 60%, 90%);
  color: hsl(116, 30%, 25%);
}

.recommand-judgement {
  background: hsl(230, 70%, 90%);
  color: hsl(230, 45%, 30%);
}

.recommand-remove {
  background: hsl(350, 70%, 90%);
  color: hsl(350, 45%, 30%);
}
```

```{r diagose}
# Number of observations
N <- NROW(reportData)

# sampling with sample_percent
if (sample_percent < 100) {
  N_sample <- ceiling(N * sample_percent / 100)
  idx <- sample(seq(N), size = N_sample)
  
  reportData <- reportData[idx, ]
} else {
  N_sample <- N
}

# solve the overview
ov <- overview(reportData)

# diagnose the missing & unique
diagn_na_unique <- diagnose(reportData)

# diagnose the numeric
diagn_numeric <- diagnose_numeric(reportData)

tab_warning <- data.frame(
  warnings = character(5000), status = character(5000), variables = character(5000),
  types = character(5000), indicator = numeric(5000), ratio = numeric(5000), 
  recommand = character(5000), stringsAsFactors = FALSE)

# duplicate --------------------------------------------------------------------
idx_last <- 0
n_duplicate <- length(attr(ov, "duplicate"))

if (n_duplicate > 0) {
  idx <- 1
  
  tab_warning$status[idx]    <- "duplicate"
  tab_warning$variables[idx] <- NA
  tab_warning$types[idx] <- NA  
  tab_warning$indicator[idx] <- n_duplicate
  tab_warning$ratio[idx]     <- n_duplicate / N
  tab_warning$warnings[idx]  <- sprintf(
    "dataset has %s (%s%%) duplicated observations", 
    format(n_duplicate, big.mark = ","),
    round(n_duplicate / N * 100, 1))
  tab_warning$recommand[idx]  <- "check"  
} else {
  idx <- NULL
}

# missing ----------------------------------------------------------------------
idx_last <- idx_last + length(idx)

warn_miss <- diagn_na_unique %>% 
  filter(missing_count > 0) %>% 
  select(variables, types, missing_count, missing_percent) %>% 
  arrange(desc(missing_count))

if (nrow(warn_miss) > 0) {
  idx <- seq(nrow(warn_miss)) + idx_last
  
  tab_warning$status[idx]    <- "missing"
  tab_warning$variables[idx] <- warn_miss$variables
  tab_warning$types[idx]     <- warn_miss$types  
  tab_warning$indicator[idx] <- warn_miss$missing_count
  tab_warning$ratio[idx]     <- warn_miss$missing_percent / 100
  tab_warning$warnings[idx]  <- sprintf(
    "%s has %s (%s%%) missing values", warn_miss$variables,
    format(warn_miss$missing_count, big.mark = ","),
    round(warn_miss$missing_percent, 1))
  tab_warning$recommand[idx]  <- "judgement"
} else {
  idx <- NULL
}

# cardinality: identifier ------------------------------------------------------
idx_last <- idx_last + length(idx)

warn_identifier <- diagn_na_unique %>% 
  filter(unique_rate == 1) %>% 
  select(variables, types, unique_count, unique_rate)

if (nrow(warn_identifier) > 0) {
  idx <- seq(nrow(warn_identifier)) + idx_last
  
  tab_warning$status[idx]     <- "cardinality"
  tab_warning$variables[idx]  <- warn_identifier$variables
  tab_warning$types[idx]      <- warn_identifier$types    
  tab_warning$indicator[idx]  <- warn_identifier$unique_count
  tab_warning$ratio[idx]      <- warn_identifier$unique_rate 
  tab_warning$warnings[idx]   <- sprintf(
    "%s has high(%.2f) cardinality, Maybe identifier",
    warn_identifier$variables, warn_identifier$unique_rate)
  tab_warning$recommand[idx]  <- "check"  
} else {
  idx <- NULL
}

# cardinality: constant --------------------------------------------------------
idx_last <- idx_last + length(idx)

warn_constant <- diagn_na_unique %>% 
  filter(unique_count == 1) %>% 
  select(variables, types, unique_count, unique_rate)

if (nrow(warn_constant) > 0) {
  idx <- seq(nrow(warn_constant)) + idx_last
  
  tab_warning$status[idx]     <- "cardinality"
  tab_warning$variables[idx]  <- warn_constant$variables
  tab_warning$types[idx]      <- warn_constant$types   
  tab_warning$indicator[idx]  <- warn_constant$unique_count
  tab_warning$ratio[idx]      <- warn_constant$unique_rate 
  tab_warning$warnings[idx]   <- sprintf(
    "%s has constant value \"%s\"",
    warn_constant$variables, 
    reportData[1, warn_constant$variables %>% as.character()] %>% 
      t() %>% 
      as.vector()
    )  
  tab_warning$recommand[idx]  <- "remove"
} else {
  idx <- NULL
}

# cardinally: high cardinality(category) ---------------------------------------
idx_last <- idx_last + length(idx)

warn_unique_cat <- diagn_na_unique %>% 
  filter(types %in% c("character", "factor", "ordered", "Date", "POSIXct")) %>%
  filter(unique_rate >= thres_uniq_cat & unique_rate < 1) %>%
  select(variables, types, unique_count, unique_rate)

if (nrow(warn_unique_cat) > 0) {
  idx <- seq(nrow(warn_unique_cat)) + idx_last
  
  tab_warning$status[idx]     <- "cardinality"
  tab_warning$variables[idx]  <- warn_unique_cat$variables
  tab_warning$types[idx]      <- warn_unique_cat$types   
  tab_warning$indicator[idx]  <- warn_unique_cat$unique_count
  tab_warning$ratio[idx]      <- warn_unique_cat$unique_rate 
  tab_warning$warnings[idx]   <- sprintf(
    "%s has a high cardinality. %s (%s%%) distinct values",
    warn_unique_cat$variables, 
    format(warn_unique_cat$unique_count, big.mark = ","),
    round(warn_unique_cat$unique_rate * 100, 1))  
  tab_warning$recommand[idx]  <- "judgement"
} else {
  idx <- NULL
}

# cardinally: low cardinality(numerical) ---------------------------------------
warn_unique_num <- diagn_na_unique %>% 
  filter(types %in% c("numeric", "integer")) %>%
  filter(unique_count <= thres_uniq_num & unique_count > 1) %>%
  select(variables, types, unique_count, unique_rate)

if (nrow(warn_unique_num) > 0) {
  idx <- seq(nrow(warn_unique_num)) + idx_last
  
  tab_warning$status[idx]     <- "cardinality"
  tab_warning$variables[idx]  <- warn_unique_num$variables
  tab_warning$types[idx]      <- warn_unique_num$types   
  tab_warning$indicator[idx]  <- warn_unique_num$unique_count
  tab_warning$ratio[idx]      <- warn_unique_num$unique_rate 
  tab_warning$warnings[idx]   <- sprintf(
    "%s has a low cardinality. %s (%s%%) distinct values",
    warn_unique_num$variables, 
    format(warn_unique_num$unique_count, big.mark = ","),
    round(warn_unique_num$unique_rate * 100, 1))  
  tab_warning$recommand[idx]  <- "judgement"
} else {
  idx <- NULL
}

# zeros ------------------------------------------------------------------------
idx_last <- idx_last + length(idx)

if (!is.null(diagn_numeric)) {
  warn_zero <- diagn_numeric %>% 
  filter(zero > 0) %>% 
  select(variables, zero) %>% 
  arrange(desc(zero))

  if (nrow(warn_zero) > 0) {
    idx <- seq(nrow(warn_zero)) + idx_last
  
    tab_warning$status[idx]     <- "zero"
    tab_warning$variables[idx]  <- warn_zero$variables
    tab_warning$types[idx]      <- NA  
    tab_warning$indicator[idx]  <- warn_zero$zero
    tab_warning$ratio[idx]      <- warn_zero$zero / N 
    tab_warning$warnings[idx]   <- sprintf(
      "%s has %s (%s%%) zeros", warn_zero$variables, 
      format(warn_zero$zero, big.mark = ","), round(warn_zero$zero / N * 100, 2))  
    tab_warning$recommand[idx]  <- "check"
  } else {
    idx <- NULL
  }
} else {
  idx <- NULL
}


# cardinally: negative ---------------------------------------------------------
idx_last <- idx_last + length(idx)

if (!is.null(diagn_numeric)) {
  warn_minus <- diagn_numeric %>% 
    filter(minus > 0) %>% 
    select(variables, minus) %>% 
    arrange(desc(minus))
  
  if (nrow(warn_minus) > 0) {
    idx <- seq(nrow(warn_minus)) + idx_last
    
    tab_warning$status[idx]     <- "negative"
    tab_warning$variables[idx]  <- warn_minus$variables
    tab_warning$types[idx]      <- NA    
    tab_warning$indicator[idx]  <- warn_minus$minus
    tab_warning$ratio[idx]      <- warn_minus$minus / N 
    tab_warning$warnings[idx]   <- sprintf(
      "%s has %s (%s%%) negatives",
      warn_minus$variables, format(warn_minus$minus, big.mark = ","),
      round(warn_minus$minus / N * 100, 2))  
    tab_warning$recommand[idx]  <- "check"
  } else {
    idx <- NULL
  }
} else {
  idx <- NULL
}

# outlier ----------------------------------------------------------------------
idx_last <- idx_last + length(idx)

if (!is.null(diagn_numeric)) {
  warn_outlier <- diagn_numeric %>% 
    filter(outlier > 0) %>% 
    select(variables, outlier) %>% 
    arrange(desc(outlier))
  
  if (nrow(warn_outlier) > 0) {
    idx <- seq(nrow(warn_outlier)) + idx_last
    
    tab_warning$status[idx]     <- "outlier"
    tab_warning$variables[idx]  <- warn_outlier$variables
    tab_warning$types[idx]      <- NA    
    tab_warning$indicator[idx]  <- warn_outlier$outlier
    tab_warning$ratio[idx]      <- warn_outlier$outlier / N 
    tab_warning$warnings[idx]   <- sprintf(
      "%s has %s (%s%%) outliers",
      warn_outlier$variables, format(warn_outlier$outlier, big.mark = ","),
      round(warn_outlier$outlier / N * 100, 2))  
    tab_warning$recommand[idx]  <- "judgement"
  } else {
    idx <- NULL
  }
} else {
  idx <- NULL
}

tab_warning <- tab_warning %>% 
  filter(status != "")
```

# Overview
## Data Structures

```{r overview-pre, results='asis'}
tab_left <- ov[1:9, ]
tab_right <- ov[10:nrow(ov), ]
rownames(tab_right) <- seq(nrow(tab_right))

tab_left <- tab_left %>% 
  mutate(value = ifelse (metrics %in% "observations", N, value)) %>%   
  mutate(value = ifelse (metrics %in% "memory size", 
                         ifelse(value / 1024^2 > 0, round(value / 1024^2),
                                round(value / 1024)), value)) %>%   
  mutate(metrics = ifelse (metrics %in% "memory size", 
                         ifelse(value / 1024^2 > 0, "memory size (MB)",
                                "memory size (KB)"), metrics))

knitr::kables(format = "html",
  list(
    knitr::kable(tab_left, digits = 2, format = "html", valign = "t",
                 format.args = list(big.mark = ","),
                 table.attr = "style=\"margin-right:40px !important;\"") %>% 
      kable_styling(full_width = FALSE, font_size = 15), 
    knitr::kable(tab_right, digits = 2, format = "html", valign = "t",
                 format.args = list(big.mark = ",")) %>% 
      kable_styling(full_width = FALSE, font_size = 15) 
    ),
  caption = "Data structures and types") %>% 
  gsub("font-size: initial !important;",
       "font-size: 12px !important;", .) %>%
  cat()
```

## Job Informations

```{r overview-job, results='asis'}
division <- c("dataset" ,"dataset", "job", "job", "job")
metrics <- c("dataset" ,"dataset type", "samples", "created", "created by")

value <- c("$dataset$", 
           "$datatype$",
           paste0(format(N_sample, big.mark = ","), " / ", 
                  format(N, big.mark = ","), " (", sample_percent, "%)"),
           "$date$",
           ifelse(author == "", "dlookr", author))

info_job <- data.frame(division = division, metrics = metrics, value = value)

cap <- "Job informations"

print_tab(info_job, caption = cap)
```

## Warnings

```{r warnings-summary, results='asis'}
if (NROW(tab_warning) < 1) {
  html_cat("No warnings")
} else {
  tab <- tab_warning %>%
    count(recommand) %>% 
    right_join(data.frame(recommand = c("check", "judgement", "remove")),
               by = "recommand") %>% 
    tidyr::spread(recommand, n) %>% 
    mutate_all(function(x) ifelse(is.na(x), 0, x))

  knitr::kable(tab, format = "html", caption = "Summary of warnings",
               col.names = c("checks", "judgements", "removes"),
               format.args = list(big.mark = ",")) %>% 
    kableExtra::kable_styling(full_width = TRUE, font_size = 14, 
                              position = "left") %>% 
    gsub("font-size: initial !important;",
         "font-size: 12px !important;", .) %>%
      cat()
}
```

```{r warnings, results='asis'}
tab_warning <- tab_warning %>% 
  select(warnings, status, recommand)

if (NROW(tab_warning) > 0) {
  cap <- "Warnings in dataset and variables"
  
  print_tab(tab_warning, caption = cap, n_rows = 22, add_row = 6)
} else {
  html_cat("No warnings in dataset and variables")
  break_page_asis()
}
```

## Variables

```{r variables, results='asis'}
cap <- "List of variables diagnosis"

html_paged_variable(reportData, caption = cap, n_rows = 25)
```

$content_missing$
# Missing Values
## List of Missing Values

```{r missing-list, results='asis'}
cap <- "List of variables including missing values"

html_paged_missing(diagn_na_unique, caption = cap, n_rows = 23, add_row = 5)
```

## Visualization

```{r missing-viz, dpi=400, fig.height=9, fig.width=9, out.width="80%", results='asis'}
diagn_missing <- diagn_na_unique %>% 
  filter(missing_count > 0)

if (NROW(diagn_missing) > 1) {
  break_line_asis(1)
  plot_na_intersect(reportData, base_family = base_family)
} else if (NROW(diagn_missing) == 1) {
  html_cat("Supported only when the number of variables including missing values is 2 or more.")
  break_line_asis(1)
} else {
  html_cat("No variables including missing values")
  break_line_asis(1)
}

break_page_asis()
```
$content_missing$

# Unique Values
## Categorical Vaiables

```{r unique-date-category, results='asis'}
html_paged_unique_cat(diagn_na_unique, thres_uniq_cat, n_rows = 25, add_row = 4)  
```

## Numerical Vaiables

```{r unique-data-numeric, results='asis'}
html_paged_unique_num(diagn_na_unique, thres_uniq_num, n_rows = 24, add_row = 5)  
```

# Categorical Variable Diagnosis
## Top Ranks

```{r diagnose-catagory, results='asis'}
in_category <- find_class(reportData, type = "date_categorical2") %>%
  length() %>% 
  as.logical()

if (in_category) {
  diagn_category <- html_paged_toprank(reportData, top = 10, type = "n")
  
  cap <- "Top 10 levels of categorical variables"
  
  print_tab(diagn_category, caption = cap, n_rows = 25, add_row = 4)
} else {
  html_cat("No categorical variable")
  break_page_asis()
}
```

# Numerical Variable Diagnosis
## Distributions

```{r diagnose-numeric, results='asis'}
diagn_numeric <- diagnose_numeric(reportData)

if (NROW(diagn_numeric) > 0) {
  cap <- "General list of numerical diagnosis"
  
  print_tab(diagn_numeric, caption = cap, font_size = 13, n_rows = 25, add_row = 4)
} else {
  html_cat("No numerical variable")
  break_page_asis()  
}
```

$content_zero$
### Zero Values

```{r numeric-zero, results='asis'}
if (NROW(diagn_numeric) > 0) {
  diagn_zero <- diagn_numeric %>%
    filter(zero > 0) %>%
    select(variables, min, median, max, zero) %>%
    mutate(`zero (%)` = round(zero / N * 100, 1)) %>%
    arrange(desc(zero))

  if (NROW(diagn_zero) > 0) {
    cap <- "List of numerical diagnosis (zero)"
  
    print_tab(diagn_zero, caption = cap, n_rows = 25, add_row = 4)
  } else {
    html_cat("No numeric variable with zero value")
    break_page_asis()      
  }
} else {
  html_cat("No numerical variable")
  break_page_asis()    
}
```
$content_zero$

$content_minus$

### Negative Values

```{r numeric-minus, results='asis'}
if (NROW(diagn_numeric) > 0) {
  diagn_minus <- diagn_numeric %>%
    filter(minus > 0) %>%
    select(variables, min, median, max, minus) %>%
    mutate(`minus (%)` = round(minus / N * 100, 1)) %>%
    arrange(desc(minus))

  if (NROW(diagn_minus) > 0) {
    cap <- "List of numerical diagnosis (minus)"
  
    print_tab(diagn_minus, caption = cap, n_rows = 25, add_row = 4)
  } else {
    html_cat("No numeric variable with negative value")
    break_page_asis()   
  }
} else {
  html_cat("No numerical variable")
  break_page_asis()     
}
```
$content_minus$

## Outliers
### List of Outliers

```{r outliers, results='asis'}
if (NROW(diagn_numeric) > 0) {
  diagn_outlier <- diagn_numeric %>%
    filter(outlier > 0) %>%
    select(variables, min, median, max, outlier) %>%
    mutate(`outlier (%)` = round(outlier / N * 100, 1)) %>%
    arrange(desc(outlier))

  if (NROW(diagn_outlier) > 0) {
    cap <- "Diagnosis of numerical variable outliers"
  
    print_tab(diagn_outlier, caption = cap, n_rows = 25, add_row = 4)
  } else {
    html_cat("No numeric variables including outliers")
    break_page_asis() 
  }
} else {
  html_cat("No numerical variable")
  break_page_asis() 
}
```

### Individual Outliers

```{r detail-outliers, fig.height=4, fig.width=6, results='asis'}
if (NROW(diagn_numeric) > 0) {
  diagn_outlier2 <- reportData %>%
    diagnose_outlier(diagn_outlier$variables)

  cols <- c("Outliers count", "Outliers ratio (%)", "Mean of outliers",
            "Mean with outliers", "Mean without outliers")

  if (NROW(diagn_outlier2) > 0) {
    variables <- diagn_outlier2 %>%
      select(variables) %>%
      unlist

    for (i in seq(variables)) {
      cap <- sprintf("variable: %s", variables[i])
      cat(sprintf("<h3>%s</h3>", cap))

      outlier_df <- data.frame(Measures = cols,
                               Values = as.vector(t(diagn_outlier2[i, -1])))
      
      values <- outlier_df$Values

      outlier_df$Values[1] <- round(values[1]) %>% 
        format(big.mark = ",")
      outlier_df$Values[2] <- round(values[2], 2) %>% 
        as.character() %>% 
        paste0("%")
      outlier_df$Values[3] <- values[3] %>% 
        format() %>% 
        as.character()
      outlier_df$Values[4] <- values[4] %>% 
        format() %>% 
        as.character()
      outlier_df$Values[5] <- values[5] %>% 
        format() %>% 
        as.character()
        
      knitr::kable(outlier_df, digits = 2, caption = variables[i], format = "html",
                   table.attr = "class=\"table table-width\"", align = "lr") %>% 
        kable_styling(full_width = FALSE, font_size = 14, position = "center") %>% 
        gsub("font-size: initial !important;",
             "font-size: 12px !important;", .) %>%
        cat()

      cat("<br><br>")
      
      plot_outlier(reportData, variables[i], base_family = base_family)
      
      break_page_asis()
    }
  } else {
    html_cat("No numeric variables including outliers")
  }
} else {
  html_cat("No numerical variable")
}
```

