---
title: "$title$"
subtitle: "$subtitle$"
abstract-title: "$abstract_title$"
abstract: "$abstract$"
date: "`r Sys.Date()`"
output: 
  dlookr::dlookr_$theme$_paged: 
    # Change to point to your cover file
    front_cover: $cover$
    toc: true
    # Change to true to add number in front of chapters
    number_sections: false
    # Change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: true
# Set  toc title, default none
toc-title: Contents
#knit: pagedown::chrome_print
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      collapse = FALSE,
                      comment = "#>",
                      fig.align = "center")
knitr::opts_chunk$set(fig.width = 12, fig.height = 9)
```

```{r packages, include=FALSE, message=FALSE, warning=FALSE}
# Load required packages for charts with UNHCR style 
library(dplyr)
library(ggplot2)
library(kableExtra)
library(dlookr)
library(htmltools)
library(reactable)

reportData <- get("reportData", .dlookrEnv)
targetVariable <- get("targetVariable", .dlookrEnv)
sample_percent <- get("sample_percent", .dlookrEnv)
author <- get("author", .dlookrEnv)
base_family <- get("base_family", .dlookrEnv)
```


```{css, echo=FALSE}
.pagedjs_page.pagedjs_first_page .pagedjs_margin-top-right>.pagedjs_margin-content::after {
    content: url("$logo$");
}

.title {
  color: $title_color$;
}

.subtitle {
  color: $subtitle_color$;
  font-size: 2.5em !important;
}
```

# Overview
## Data Structures

```{r overview-pre, results='asis'}
# Number of observations
N <- NROW(reportData)

# sampling with sample_percent
if (sample_percent < 100) {
  N_sample <- ceiling(N * sample_percent / 100)
  idx <- sample(seq(N), size = N_sample)
  
  reportData <- reportData[idx, ]
} else {
  N_sample <- N
}

if (length(targetVariable) == 0) targetVariable <- NULL
```

```{r overview, results='asis'}
# solve the overview
ov <- overview(reportData)

tab_left <- ov[1:9, ]
tab_right <- ov[10:nrow(ov), ]
rownames(tab_right) <- seq(nrow(tab_right))

tab_left <- tab_left %>% 
  mutate(value = ifelse (metrics %in% "observations", N, value)) %>%   
  mutate(value = ifelse (metrics %in% "memory size", 
                         ifelse(value / 1024^2 > 0, round(value / 1024^2),
                                round(value / 1024)), value)) %>%   
  mutate(metrics = ifelse (metrics %in% "memory size", 
                         ifelse(value / 1024^2 > 0, "memory size (MB)",
                                "memory size (KB)"), metrics))

knitr::kables(format = "html",
  list(
    knitr::kable(tab_left, digits = 2, format = "html", valign = "t",
                 format.args = list(big.mark = ","),
                 table.attr = "style=\"margin-right:40px !important;\"") %>% 
      kable_styling(full_width = FALSE, font_size = 15), 
    knitr::kable(tab_right, digits = 2, format = "html", valign = "t",
                 format.args = list(big.mark = ",")) %>% 
      kable_styling(full_width = FALSE, font_size = 15) 
    ),
  caption = "Data structures and types") %>% 
  gsub("font-size: initial !important;",
       "font-size: 12px !important;", .) %>%  
  cat()
```

## Job Informations

```{r overview-job, results='asis'}
division <- c("dataset" ,"dataset" ,"dataset", "job", "job", "job")
metrics <- c("dataset" ,"dataset type", "target", "samples", 
             "created", "created by")

value <- c("$dataset$", 
           "$datatype$",
           ifelse(is.null(targetVariable), "not defied", targetVariable),
           paste0(format(N_sample, big.mark = ","), " / ", 
                  format(N, big.mark = ","), " (", sample_percent, "%)"),
           "$date$",
           ifelse(author == "", "dlookr", author))

info_job <- data.frame(division = division, metrics = metrics, value = value)

cap <- "Job informations"

print_tab(info_job, caption = cap)
```

```{r check_variables}
idx.numeric <- find_class(reportData, type = "numerical")
nm.numeric <- find_class(reportData, type = "numerical", index = FALSE)

if (!is.null(targetVariable)) {
  # remove target variable from variable index
  idx.numeric <- idx.numeric[nm.numeric != targetVariable]
  
  factor_flag <- class(pull(reportData, targetVariable))[1] %in% c("factor", "ordered")
  numeric_flag <- class(pull(reportData, targetVariable))[1] %in% c("integer", "numeric")
  
  target <- if (!factor_flag & numeric_flag) 
    factor(pull(reportData, targetVariable)) else
      pull(reportData, targetVariable)
} else { 
  factor_flag <- FALSE
}

# if all elements of a numerical variable are NA,
# remove from correlation coefficient calculation
idx.numeric <- idx.numeric[apply(as.data.frame(reportData[, idx.numeric]), 2,
                                 function(x) !all(is.na(x)))]

# if all elements of the numerical variable are the same value,
# remove from the correlation coefficient calculation
idx.numeric <- idx.numeric[apply(as.data.frame(reportData[, idx.numeric]), 2,
                                 function(x) diff(range(x, na.rm = TRUE)) > 0)]
```

# Univariate Analysis
## Descriptive Statistics
### Numerical Variables

```{r descriptive-numerical, results='asis'}
cap <- "Descriptive statistics of numerical variables"

html_paged_describe(reportData, caption = cap, font_size = 13)
```

```{r descriptive-numerical-detail, results='asis', dpi=300, fig.height=5, fig.width=5, out.width="80%"}
# cap <- "Descriptive Statistics of Numerical Variables"
html_paged_describe_detail(reportData, base_family = base_family)
```

### Categorical Variables

```{r descriptive-categorical, results='asis'}
cap <- "Top rank levels of categorical variables"

html_paged_categorical(reportData, caption = cap, font_size = 13)
```

```{r descriptive-categorical-detail, results='asis', dpi=300, fig.height=5, fig.width=5, out.width="80%"}
# cap <- "Descriptive Statistics of Categorical Variables"
html_paged_categorical_detail(reportData, base_family = base_family)
```

## Normality Test
```{r normality, results='asis'}
cap <- "Descriptive statistics of numerical variables"

html_paged_normality(reportData, caption = cap, font_size = 13)
```

```{r normality-detail, results='asis', dpi=300, fig.height=5, fig.width=7, out.width="90%"}
suppressWarnings({
  html_paged_normality_detail(reportData, base_family = base_family)
})
```


# Bivariate Analysis
## Compare Numerical Variables
```{r compare-numerical, results='asis'}
cap <- "Correlation coefficient"

html_paged_compare_numerical(reportData, caption = cap, font_size = 13, base_family = base_family)
```

## Compare Categorical Variables
```{r compare-categorical, results='asis', dpi=300, fig.height=5, fig.width=5, out.width="70%"}
cap <- "Chisqure-test"

html_paged_compare_categorical(reportData, caption = cap, font_size = 13, base_family = base_family)
```

# Multivariate Analysis
## Correlation Analysis
### Correlation Coefficient Matrix

```{r correlation, results='asis'}
html_paged_correlation(reportData) 
```

### Correlation Plot

```{r plot-correlation, results='asis', dpi=300, fig.height=7, fig.width=7, out.width="100%"}
if (length(idx.numeric) < 2) {
  html_cat("The number of numerical variables is less than 2.")
} else {
  dlookr::plot_correlate(reportData, base_family = base_family)  
}

break_page_asis()
```

$targeted_eda$

# Target based Analysis
## Target Variable and Numerical Variables

```{r group-numerical, results='asis', dpi=400, fig.height=5, fig.width=7, out.width="80%"}
html_paged_target_numerical(reportData, targetVariable, base_family = base_family)  
```

## Target Variable and Categorical Variables

```{r group-categorical, results='asis', dpi=400, fig.height=5, fig.width=7, out.width="80%"}
html_paged_target_categorical(reportData, targetVariable, base_family = base_family)  
```

```{r group-correlation, results='asis', dpi=400, fig.height=6, fig.width=6, out.width="95%"}
if (!is.null(targetVariable) & factor_flag) {
  htmltools::h2("Grouped Correlation")
  
  html_paged_target_correlation(reportData, targetVariable, base_family = base_family)  
}  
```

$targeted_eda$
